PANCHANGE_analysis

### 2020-09-25 PANCHANGE_analysis.Rmd
changed time variable in regression

```{r model1a function}
model1a.estimates <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("Disorder_hierarchical",
                            "Gender_collapsed",
                            "age_category_collapsed",
                            "Ethnicity_collapsed",
                            "time_diff_sign_up_coping"
                            )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

  assign(paste0(outcome,"model1a_estimates"),
         tidy(get(paste0(outcome,".model1a")), conf.int = TRUE) %>%
           mutate(
             "Indepent variable" = recode_factor(
               term,
               "(Intercept)" = "Intercept",
               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
               "Disorder_hierarchicalEating disorders" = "Eating disorders",
               "Disorder_hierarchicalOCDs" = "OCDs",
               "Disorder_hierarchicalPTSD" = "PTSD",
               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
               "Gender_collapsedFemale" = "Female",
               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
               "age_category_collapsed19-25" = "19-25 years",
               "age_category_collapsed26-35" = "26-35 years",
               "age_category_collapsed36-45" = "36-45 years",
               "age_category_collapsed46-55" = "46-55 years",
               "age_category_collapsed56-65" = "56-65 years",
               "age_category_collapsed66-70" = "66-70 years",
               "age_category_collapsed71-75" = "71-75 years",
               "age_category_collapsed76+" = "76+ years",
               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
               "Ethnicity_collapsedAfrican or African British" = "African or African British",
               "Ethnicity_collapsedOther" = "Other ethnicity",
               "time_diff_sign_up_coping" = "Time difference: prepandemic to COPING"
             ),
             "Estimate" = format(
               round(estimate,
                     digits = 2),
               nsmall = 2),
             "95% CI low" = format(
               round(conf.low,
                     digits = 2),
               nsmall = 2),
             "95% CI up" = format(
               round(conf.high,
                     digits = 2),
               nsmall = 2),
             "SE" = format(
               round(std.error,
                     digits = 2),
               nsmall = 2),
             "z score" = format(
               round(statistic,
                     digits = 2),
               nsmall = 2),
             "p value" = case_when(
               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
             )
           ) %>%
           select(
             "Indepent variable",
             "Estimate",
             "95% CI low",
             "95% CI up",
             "SE",
             #    "z score",
             "p value"
           )
  )

@@

```{r model1b function}
model1b.estimates <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "time_diff_sign_up_coping"
                                )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

               "time_diff_sign_up_coping" = "Time difference: prepandemic to COPING"

@@

```{r model1a.explan function}
model1a.explan.estimates <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "Disorder_hierarchical",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "time_diff_sign_up_coping"
  )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

  assign(paste0(outcome,".",explan_var,"model1a.explan_estimates"),
         tidy(get(paste0(outcome,".",explan_var,".model1a.explan")), conf.int = TRUE) %>%
           mutate(
             "Indepent variable" = recode_factor(
               term,
               "(Intercept)" = "Intercept",
               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
               "Disorder_hierarchicalEating disorders" = "Eating disorders",
               "Disorder_hierarchicalOCDs" = "OCDs",
               "Disorder_hierarchicalPTSD" = "PTSD",
               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
               "Gender_collapsedFemale" = "Female",
               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
               "age_category_collapsed19-25" = "19-25 years",
               "age_category_collapsed26-35" = "26-35 years",
               "age_category_collapsed36-45" = "36-45 years",
               "age_category_collapsed46-55" = "46-55 years",
               "age_category_collapsed56-65" = "56-65 years",
               "age_category_collapsed66-70" = "66-70 years",
               "age_category_collapsed71-75" = "71-75 years",
               "age_category_collapsed76+" = "76+ years",
               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
               "Ethnicity_collapsedAfrican or African British" = "African or African British",
               "Ethnicity_collapsedOther" = "Other ethnicity",
               "time_diff_sign_up_coping" = "Time difference: prepandemic to COPING"
             ),
             "Estimate" = format(
               round(estimate,
                     digits = 2),
               nsmall = 2),
             "95% CI low" = format(
               round(conf.low,
                     digits = 2),
               nsmall = 2),
             "95% CI up" = format(
               round(conf.high,
                     digits = 2),
               nsmall = 2),
             "SE" = format(
               round(std.error,
                     digits = 2),
               nsmall = 2),
             "z score" = format(
               round(statistic,
                     digits = 2),
               nsmall = 2),
             "p value" = case_when(
               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
             )
           ) %>%
           select(
             "Indepent variable",
             "Estimate",
             "95% CI low",
             "95% CI up",
             "SE",
             #    "z score",
             "p value"
           )
  )

@@

```{r model1b.explan function}
model1b.explan.estimates <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "time_diff_sign_up_coping"
  )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

>>>>

```{r model1a function}
model1a.estimates <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("Disorder_hierarchical",
                            "Gender_collapsed",
                            "age_category_collapsed",
                            "Ethnicity_collapsed",
                            "time_diff_coping_lockdown_march_23"
                            )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

  assign(paste0(outcome,"model1a_estimates"),
         tidy(get(paste0(outcome,".model1a")), conf.int = TRUE) %>%
           mutate(
             "Indepent variable" = recode_factor(
               term,
               "(Intercept)" = "Intercept",
               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
               "Disorder_hierarchicalEating disorders" = "Eating disorders",
               "Disorder_hierarchicalOCDs" = "OCDs",
               "Disorder_hierarchicalPTSD" = "PTSD",
               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
               "Gender_collapsedFemale" = "Female",
               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
               "age_category_collapsed19-25" = "19-25 years",
               "age_category_collapsed26-35" = "26-35 years",
               "age_category_collapsed36-45" = "36-45 years",
               "age_category_collapsed46-55" = "46-55 years",
               "age_category_collapsed56-65" = "56-65 years",
               "age_category_collapsed66-70" = "66-70 years",
               "age_category_collapsed71-75" = "71-75 years",
               "age_category_collapsed76+" = "76+ years",
               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
               "Ethnicity_collapsedAfrican or African British" = "African or African British",
               "Ethnicity_collapsedOther" = "Other ethnicity",
               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline"
             ),
             "Estimate" = format(
               round(estimate,
                     digits = 2),
               nsmall = 2),
             "95% CI low" = format(
               round(conf.low,
                     digits = 2),
               nsmall = 2),
             "95% CI up" = format(
               round(conf.high,
                     digits = 2),
               nsmall = 2),
             "SE" = format(
               round(std.error,
                     digits = 2),
               nsmall = 2),
             "z score" = format(
               round(statistic,
                     digits = 2),
               nsmall = 2),
             "p value" = case_when(
               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
             )
           ) %>%
           select(
             "Indepent variable",
             "Estimate",
             "95% CI low",
             "95% CI up",
             "SE",
             #    "z score",
             "p value"
           )
  )

@@

```{r model1b function}
model1b.estimates <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "time_diff_coping_lockdown_march_23"
                                )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline"

@@

```{r model1a.explan function}
model1a.explan.estimates <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "Disorder_hierarchical",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "time_diff_coping_lockdown_march_23"
  )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

  assign(paste0(outcome,".",explan_var,"model1a.explan_estimates"),
         tidy(get(paste0(outcome,".",explan_var,".model1a.explan")), conf.int = TRUE) %>%
           mutate(
             "Indepent variable" = recode_factor(
               term,
               "(Intercept)" = "Intercept",
               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
               "Disorder_hierarchicalEating disorders" = "Eating disorders",
               "Disorder_hierarchicalOCDs" = "OCDs",
               "Disorder_hierarchicalPTSD" = "PTSD",
               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
               "Gender_collapsedFemale" = "Female",
               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
               "age_category_collapsed19-25" = "19-25 years",
               "age_category_collapsed26-35" = "26-35 years",
               "age_category_collapsed36-45" = "36-45 years",
               "age_category_collapsed46-55" = "46-55 years",
               "age_category_collapsed56-65" = "56-65 years",
               "age_category_collapsed66-70" = "66-70 years",
               "age_category_collapsed71-75" = "71-75 years",
               "age_category_collapsed76+" = "76+ years",
               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
               "Ethnicity_collapsedAfrican or African British" = "African or African British",
               "Ethnicity_collapsedOther" = "Other ethnicity",
               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline"
             ),
             "Estimate" = format(
               round(estimate,
                     digits = 2),
               nsmall = 2),
             "95% CI low" = format(
               round(conf.low,
                     digits = 2),
               nsmall = 2),
             "95% CI up" = format(
               round(conf.high,
                     digits = 2),
               nsmall = 2),
             "SE" = format(
               round(std.error,
                     digits = 2),
               nsmall = 2),
             "z score" = format(
               round(statistic,
                     digits = 2),
               nsmall = 2),
             "p value" = case_when(
               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
             )
           ) %>%
           select(
             "Indepent variable",
             "Estimate",
             "95% CI low",
             "95% CI up",
             "SE",
             #    "z score",
             "p value"
           )
  )

@@

```{r model1b.explan function}
model1b.explan.estimates <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "time_diff_coping_lockdown_march_23"
  )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula
